Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-01 paper/disc20clustering.tex
Comments

\begin{proof}
	Fix any online algorithm \ALG{}.
	Let $I(C)$ denote the cluster where nodes of ground set $C$ are located initially.
	\maciek{A problem with the definition! The first pair does not have the same initial location of its nodes.}
	Initially all nodes are single (they belong to their own trivial ground sets).

@@

	Finally, we bound the cost of \OPT.
	Given this sequence of requests,
	\OPT migrates $\set{x_0,y_0}$ to the cluster $I(x^*)$ by
	swapping $\set{x_0,y_0}$ with $\set{x^*,y^*}$.
	Hence,
	OPT pays for $2$ node swaps and
	\ALG{} incurs at least one swap for each node in the sequence $X := x_0, x_1,\dots$.
	We exclude at most $(k-1) + ( \ell+1)$ nodes out of $k \cdot \ell$ nodes,
	therefore $|X| \geq k \cdot \ell - k - \ell$ \maciek{elaborate on exclusion?}.
	Finally, $\ALG/\OPT \geq (k \cdot \ell - k - \ell) / 2\in \Omega(k\cdot\ell)$.
\end{proof}

>>>>

\begin{proof}
	\maciek{Better name than $S_1$?}
	Fix any online algorithm \ALG{}.
	Let $I(C)$ denote the cluster where nodes of ground set $C$ are located initially.
	\maciek{A problem with the definition! The first pair does not have the same initial location of its nodes.}
	Initially all nodes are single (they belong to their own trivial ground sets).

@@

	Finally, we bound the cost of \OPT.
	Given this sequence of requests,
	\OPT migrates $\set{x_0,y_0}$ to the cluster $I(x^*)$ by
	swapping $\set{x_0,y_0}$ with $\set{x^*,y^*}$.
	Hence,
	OPT pays for $2$ node swaps and
	\ALG{} incurs at least one swap for each node in the sequence $X := x_0, x_1,\dots$.
	We exclude at most $(k-1) + ( \ell+1)$ nodes out of $k \cdot \ell$ nodes,
	therefore $|X| \geq k \cdot \ell - k - \ell$ \maciek{elaborate. Don't use the word "exclude" unless very obvious. Just sum up the real cost.}.
	Finally, $\ALG/\OPT \geq (k \cdot \ell - k - \ell) / 2\in \Omega(k\cdot\ell)$.
\end{proof}
